---
title: "cefitds"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

CEFI THREDDS catalog navigation using R

# Requirements

### CRAN 
  + [R v4.1+](https://www.r-project.org/)
  
  + [thredds](https://CRAN.R-project.org/package=thredds)
	
### Github
  + [cefi](https://github.com/BigelowLab/cefi)
  
# Suggested
  + [httr](https://CRAN.R-project.org/package=httr)

# Installation

```
remotes::install_github("BigelowLab/cefitds")
```

# Usage

Retrieve DatasetNode objects for a specific region, product suite and set of variables.  Each object contains the URL for the NetCDF connection.

## Query the THREDDS catalog

```{r usage}
suppressPackageStartupMessages({
  library(cefitds)
  library(tidync)
  library(dplyr)
})

nodes = query_cefi(region = "northwest_atlantic",
                   product = "hindcast",
                   period = "monthly",
                   vars = c("btm_o2", "btm_temp"))
nodes
```


#### As a table

You can transform the above to be a simpler table.

```{r table}
table = query_cefi(region = "northwest_atlantic",
                   product = "hindcast",
                   period = "monthly",
                   vars = c("btm_o2", "btm_temp"),
                   as = "table")
dplyr::glimpse(table)
```

#### As a CEFI catalog
Or perhaps more useful as catalog CEFI records.

```{r catalog}
catalog = query_cefi(region = "northwest_atlantic",
                   product = "hindcast",
                   period = "monthly",
                   vars = c("btm_o2", "btm_temp"),
                   as = "catalog")
dplyr::glimpse(catalog)
```


It is this latter you can use to access data.  Below we show how to open the dataset, but to do more see the documentation for the [cefi R package](https://github.com/BigelowLab/cefi).


```{r cefi_open}
x = cefi::cefi_open(dplyr::slice(catalog, 1))
x
```